---
title: "Recent News"
site: distill::distill_website
listing: posts
---




```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(distill)
library(tidyverse)
#create_post("Post-1", draft = TRUE)

library(bs4cards) # To install before
# install.packages("devtools")
#devtools::install_github("djnavarro/bs4cards")

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html



```



```{r, layout="l-page"}
slickR::slickR(
    list.files("figures/banner",full.names = TRUE,pattern = 'jpeg'),
    height = 500,
    width = '100%')
```


## ICE/IAMOT Conference Nancy 2022


In 2020 and 2021 successively, two of the leading communities on Management of Technology, Engineering and Innovation organized on-line versions of their scientific conferences, showing much-needed adaptability in a pandemic situation.
 
In 2022, for the first time ever these two communities will work together for their annual meeting, aiming to explore new ways for these technology management and innovation communities to interact and come up with innovative solutions to the critical global issues of our time.

This joint event will be the place where research, science and industry innovators are invited to contribute original ideas, papers, special sessions, workshops and open initiatives. We would like to kindly invite our growing community of researchers, innovators, industrialists, engineers and practitioners to share their insights, practices, projects and case studies that address the conference theme: 

::: {.hl}
**"Technology, Engineering, and Innovation Management Communities  as Enablers for Social-Ecological Transitions"**
:::



We are looking forward to your participation!

Pr. Laure Morel, Dr Laurent Dupont & Pr. Mauricio Camargo 
ICE-IAMOT 2022 General Chairs




<iframe width="900" height="500" src="https://www.youtube.com/embed/aSeP2n7dAR8" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>


```{r, layout="l-page"}

Cards <- 
  tribble(
    ~Title, ~Description, ~Image,
    "Key Notes & Roundtables",   
      "ICE/IEEE ITMC conference includes distinguished keynote speakers. Those keynotes will participate in our panel sessions on Innovation through the use of Immersive Technologies and Artificial Intelligence. We were able to acquire a selection of thought leading innovation managers, CEOs, scholars, politicians, and entrepreneurs in these fields.",
    'https://www.ice-conference2021.org/wp-content/uploads/2019/09/roundtable-hxdbzxy-sstock.jpg',
    
    "Special Issues",   
      "ICE/IEEE ITMC is proud to announce that outstanding papers will be invited to submit an extended version in special issues organised by prestigious international journals, with fast track selection. In addition to the possibility of submitting selected papers to these journals, there is an opportunity to interact with editors.",
    'https://www.ice-conference2021.org/wp-content/uploads/2019/09/roundtable-hxdbzxy-sstock.jpg',
    
    "NITIM-Doctoral School",   
      "As usual, a three-day doctoral school, NITIM (European graduate school on Networks, Information, Technology and Innovation Management) is offered upon the ICE conference. This focuses on topics in the areas of entrepreneurship, innovation and technology management as well as ICT technologies.",
    'https://www.ice-conference2021.org/wp-content/uploads/2019/09/roundtable-hxdbzxy-sstock.jpg'
  )

Cards %>% 
  cards(
    title = Title,
    text = Description,
    image = Image
    #link = gallery_url,
    #footer = paste("Read More:", date)
  )

```

